Rubin Observatory Scheduling Algorithm and Simulations

### 2023-04-28 ms.tex

\sunbsection{Kinematic Model}

@@

@@

@@

\software{Astropy \citep{astropy2013, astropy2018}, 
          Healpy and HEALpix\footnote{\url{http://healpix.sourceforge.net}} \citep{healpix2005, Zonca2019},
          Numpy \citep{harris2020array},
          Matplotlib \citep{Hunter:2007},
          Scipy \citep{2020SciPy-NMeth},
          Pandas \citep{reback2022},
          Scikit-learn \citep{scikit-learn},
          OpenOrb \citep{Granvik2009}}

>>>>

\subsection{Kinematic Model}

@@

\begin{figure}
    \centering
    \epsscale{0.7}
    \plotone{plots/seeing_over_time.pdf} \\
    \plottwo{plots/cloudy_over_time.pdf}{plots/cloud_levels.pdf}
    \epsscale{1}
    \caption{Seeing and cloud levels.}
    \label{fig:seeing_clouds}
\end{figure}

@@

The default tesselation of the sky we employ is a (possibly) optimal solution to the covering problem based on the rotations in the icosahedral group of order 60 and determinant 1 \citep{Hardin94}.

@@

\software{Astropy \citep{astropy2013, astropy2018}, 
          Healpy and HEALpix\footnote{\url{http://healpix.sourceforge.net}} \citep{healpix2005, Zonca2019},
          Numpy \citep{harris2020array},
          Matplotlib \citep{Hunter:2007},
          Scipy \citep{2020SciPy-NMeth},
          Pandas \citep{reback2022},
          Scikit-learn \citep{scikit-learn},
          OpenOrb \citep{Granvik2009},
          GNU Parallel \citep{Tange2023}}
